Search for WIMP Inelastic Scattering Off Xenon Nuclei With XENON100

### 2017-04-24 Inelastic/analysis.tex
add all comments, final version

@@

%%%%% DEPENDING ON if we add it before %%%%%
%{\textcolor{red} {Should we also give the numerical values of $L_Y$ and $Y$?}}
The pdf of the ER and NR contributions are then convolved  to obtain the overall pdf of the expected signal.
A 2D (cS1 versus cS2) acceptance map is applied to the signal pdf to reproduce data selection effects. Acceptances are computed separately for each selection 
criteria using the $^{241}$AmBe calibration sample. Acceptances of other selections such as the liquid xenon veto cut, and the single-scatter interaction, represent an exception  for which  
a dedicated computation has been performed. The combined acceptance  of all selection criteria in the region of interest averages to $\sim$$(0.80\pm0.05)$. 
Figure~\ref{fig:SR}\,(a) shows an example of fully simulated signal model for a WIMP mass of 100\,GeV/c$^2$.

The signal simulation procedure has been validated by reproducing the 39.6\,keV xenon line from interactions due to neutrons from the 
$^{124}$AmBe source and compared to data. The simulated events were in agreement  with calibration data within statistical uncertainties. 
More detail on this validation campaign are reported in the appendix. 
%%%%%% DEPENDS on the journal  %%%%%
%{\textcolor{red} {Should we show an example, namely a figure from the signal model note?}}

@@

The distribution of the calibration sample has been compared to the data of the science run in the two control regions,
and agreement was found within statistical uncertainties. Furthermore, $^{60}$Co calibration data have been compared in the region of interest to  
data from the $^{232}$Th calibration campaign, and the largest deviation between the two shapes is within 4\%. 
%%%%% Said later anyway, propose to remove it here %%%%%
%\sout{An additional systematic uncertainty of 4\% has thus been applied to the expected background yield of each sub-region of the ROI.}

@@

\begin{figure}[t!]
  \includegraphics[width=\linewidth]{images/wimp_sys_unc.png}
\caption{Predicted signal yield in each sub-region (blue curve), along with statistical and systematic uncertainties (shaded area) simulated for a WIMP mass of 100\,GeV/c$^2$.  The signal has been scaled for a total number of 50 events.}
  \label{fig:unc}
\end{figure}

Uncertainties on the  prediction of the total number of background events arise from the uncertainty on the measurement of the normalisation 
factor, $\tau_{\text{bkg}}$, and amount to 6\%. % contribution of radiogenic neutrons are neglected. 
Systematic uncertainty on the shape of the predicted background distribution are assessed by the maximal observed discrepancy in the ROI between
the $^{60}$Co and $^{232}$Th calibration samples. The two sample's normalized yield are compared in each sub-region and the overall largest deviation (incompatible
with statistical fluctuation) is found to be within 4\%.  A  systematic uncertainty of 4\% is then assigned  to the expected yield of each sub-region.
Uncertainties belonging to different sub-regions in the ROI are considered independent from one another.

>>>>

\begin{figure*}[t!]
	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_contour.png}}
	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/test_projections.png}} 
%	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice1.png}} \\
%	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice2.png}}
%	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice3.png}}
	\caption{A simulation of the 39.6\,keV  xenon line activated from $^{241}$AmBe neutrons is compared with  data.
		 Figure~(a) compares contours of equal density in the (cS1,cS2)-plane, while Figure~(b) shows the same distribution projected in cS1 for
		 several ranges of cS2, the histograms are normalized to unit area. Light and dark blue represent simulation and data, respectively.
		}

  \label{fig:mc_comp}
\end{figure*}

@@

%%%%% DEPENDING ON if we add it before %%%%%
%{\textcolor{red} {Should we also give the numerical values of $L_Y$ and $Y$?}}
The pdf of the ER and NR contributions are then convolved  to obtain the overall pdf of the expected signal.
A 2D (cS1 versus cS2) acceptance map is applied to the signal pdf to reproduce data selection effects. Acceptances are computed separately for each selection 
criteria using the $^{241}$AmBe calibration sample. Acceptances of other selections such as the liquid xenon veto cut, and the single-scatter interaction, represent an exception  for which  
a dedicated computation has been performed. The combined acceptance  of all selection criteria in the region of interest averages to $\sim$$(0.80\pm0.05)$. 
Figure~\ref{fig:SR}\,(a) shows an example of fully simulated signal model for a WIMP mass of 100\,GeV/c$^2$, normalized to 50 events.

\input{appendix} 
%The signal simulation procedure has been validated by reproducing the 39.6\,keV xenon line from interactions due to neutrons from the 
%$^{241}$AmBe source and compared to data. The simulated events were in agreement  with calibration data within statistical uncertainties. 
%More detail on this validation campaign are reported in the appendix. 
%%%%%% DEPENDS on the journal  %%%%%
%{\textcolor{red} {Should we show an example, namely a figure from the signal model note?}}

@@

The distribution of the calibration sample has been compared to the data of the science run in the two control regions,
and agreement was found within statistical uncertainties. Furthermore, $^{60}$Co calibration data have been compared in the region of interest to  
data from the $^{232}$Th calibration campaign, and systematic uncertainties assessed based on it.
%%%%% Said later anyway, propose to remove it here %%%%%
%\sout{An additional systematic uncertainty of 4\% has thus been applied to the expected background yield of each sub-region of the ROI.}

@@

\begin{figure}[t!]
  \includegraphics[width=\linewidth]{images/wimp_sys_unc.png}
  \caption{Predicted signal yield in each sub-region (blue curve), along with statistical and systematic uncertainties (shaded area) simulated for a WIMP mass of 100\,GeV/c$^2$.  The signal has been scaled for a total number of 50 events. The sub-regions are defined in Figure~\ref{fig:SR}.}
  \label{fig:unc}
\end{figure}

Uncertainties on the  prediction of the total number of background events arise from the uncertainty on the measurement of the normalisation 
factor, $\tau_{\text{bkg}}$, and amount to 6\%. % contribution of radiogenic neutrons are neglected. 
Systematic uncertainty on the shape of the predicted background distribution are assessed by the maximal observed discrepancy in the ROI between
the $^{60}$Co and $^{232}$Th calibration samples. The two sample's normalized yield are compared in each sub-region and the overall largest deviation (incompatible
with statistical fluctuation) is found to be within 4\%.  Consequently, a systematic uncertainty of 4\% is assigned  to the expected yield of each sub-region.
Uncertainties belonging to different sub-regions in the ROI are considered independent from one another.

### 2017-04-24 Inelastic/appendix.tex
add all comments, final version

\appendix*

\section{}

\begin{figure*}[tbh!]
	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_contour.png}}
	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/test_projections.png}} 
%	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice1.png}} \\
%	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice2.png}}
%	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice3.png}}
	\caption{A simulation of the 39.6\,keV  xenon line activated from $^{243}$AmBe neutrons is compared with  data.
		 Figure~(a) compares contours of equal density in the (cS1,cS2)-plane, while Figure~(b) shows the same distribution projected in cS1 for
		 several ranges of cS2, the histograms are normalized to unit area. Light and dark blue represent simulation and data, respectively.
		}

  \label{fig:mc_comp}
\end{figure*}

The detector response to inelastic WIMP-$^{129}$Xe interactions was simulated using an empirical signal model. 
The procedure, described in detail in section~\ref{sec:signal}, takes advantage of several 
approximations that have been validated extensively. 
The main aim of the cross check was to reproduce the 39.6\,keV xenon line activated from $^{124}$AmBe neutrons with simulation.
For this purpose the NR energy spectrum expected from inelastic neutron-$^{129}$Xe scattering has been obtained via  Monte Carlo techniques, 
where we take into account the  detector response and the non-uniform spatial distribution. The Acceptance of analysis selections to this type of interaction 
have been recomputed. In particular, the acceptance to the double scatter cut differs greatly between neutrons and WIMPs scattering. 
Except for acceptances and NR energy spectrum, the simulation has been performed following the recipe described in the main text. Figure~\ref{fig:mc_comp}
shows a comparisons between simulation (light blue) and calibration data (dark blue), contour lines of equal densities are compared in Figure~(a), 
while Figure~(b) shows the cS1 projected distributions for different ranges in cS2. These considerations thus validate our analysis.

\newpage

>>>>

%\appendix*

\subsection{Signal Validation}

The detector response to inelastic WIMP-$^{129}$Xe interactions was simulated using an empirical signal model. 
The procedure, described in detail in section~\ref{sec:signal}, takes advantage of several 
approximations that have been validated extensively. 
The main aim of the cross check was to reproduce the 39.6\,keV xenon line activated from $^{241}$AmBe neutrons with simulation.
For this purpose the NR energy spectrum expected from inelastic neutron-$^{129}$Xe scattering has been obtained via  Monte Carlo techniques, 
where we take into account the  detector response and the non-uniform spatial distribution. The acceptance of analysis selections to this type of interaction 
have been recomputed. In particular, the acceptance to the double scatter cut differs greatly between neutrons and WIMPs scattering. 
Except for acceptances and NR energy spectrum, the simulation has been performed following the recipe described in the main text. Figure~\ref{fig:mc_comp}
shows a comparisons between simulation (light blue) and calibration data (dark blue), contour lines of equal densities are compared in Figure~(a), 
while Figure~(b) shows the cS1 projected distributions for different ranges in cS2. These considerations thus validate our analysis.

### 2017-04-24 Inelastic/inelastic_main.tex
add all comments, final version

@@

\title{Search for WIMP Inelastic Scattering Off Xenon Nuclei With XENON100}% Force line breaks with \\

\collaboration{The XENON100 Collaboration}\noaffiliation

@@

\input{appendix}

>>>>

\newcommand{\bern}{\affiliation{Albert Einstein Center for Fundamental Physics, University of Bern, 3012 Bern, Switzerland}}

\newcommand{\bologna}{\affiliation{Department of Physics and Astrophysics, University of Bologna and INFN-Bologna, 40126 Bologna, Italy}}

\newcommand{\chicago}{\affiliation{Department of Physics \& Kavli Institute of Cosmological Physics, University of Chicago, Chicago, IL 60637, USA}}

\newcommand{\coimbra}{\affiliation{LIBPhys, Department of Physics, University of Coimbra, 3004-516 Coimbra, Portugal}}

\newcommand{\columbia}{\affiliation{Physics Department, Columbia University, New York, NY 10027, USA}}

\newcommand{\lngs}{\affiliation{INFN-Laboratori Nazionali del Gran Sasso and Gran Sasso Science Institute, 67100 L'Aquila, Italy}}

\newcommand{\mainz}{\affiliation{Institut f\"ur Physik \& Exzellenzcluster PRISMA, Johannes Gutenberg-Universit\"at Mainz, 55099 Mainz, Germany}}

\newcommand{\heidelberg}{\affiliation{Max-Planck-Institut f\"ur Kernphysik, 69117 Heidelberg, Germany}}

\newcommand{\munster}{\affiliation{Institut f\"ur Kernphysik, Westf\"alische Wilhelms-Universit\"at M\"unster, 48149 M\"unster, Germany}}

\newcommand{\nikhef}{\affiliation{Nikhef and the University of Amsterdam, Science Park, 1098XG Amsterdam, Netherlands}}

\newcommand{\nyuad}{\affiliation{New York University Abu Dhabi, Abu Dhabi, United Arab Emirates}}

\newcommand{\purdue}{\affiliation{Department of Physics and Astronomy, Purdue University, West Lafayette, IN 47907, USA}}

\newcommand{\rpi}{\affiliation{Department of Physics, Applied Physics and Astronomy, Rensselaer Polytechnic Institute, Troy, NY 12180, USA}}

\newcommand{\rice}{\affiliation{Department of Physics and Astronomy, Rice University, Houston, TX 77005, USA}}

\newcommand{\stockholm}{\affiliation{Oskar Klein Centre, Department of Physics, Stockholm University, AlbaNova, Stockholm SE-10691, Sweden}}

\newcommand{\subatech}{\affiliation{SUBATECH, IMT Atlantique, CNRS/IN2P3, Universit\'e de Nantes, Nantes 44307, France}}

\newcommand{\torino}{\affiliation{INFN-Torino and Osservatorio Astrofisico di Torino, 10125 Torino, Italy}}

\newcommand{\ucla}{\affiliation{Physics \& Astronomy Department, University of California, Los Angeles, CA 90095, USA}}

\newcommand{\ucsd}{\affiliation{Department of Physics, University of California, San Diego, CA 92093, USA}}

\newcommand{\wis}{\affiliation{Department of Particle Physics and Astrophysics, Weizmann Institute of Science, Rehovot 7610001, Israel}}

\newcommand{\zurich}{\affiliation{Physik-Institut, University of Zurich, 8057  Zurich, Switzerland}}

\newcommand{\paris}{\affiliation{LPNHE, Université Pierre et Marie Curie, Université Paris Diderot, CNRS/IN2P3, Paris 75252, France}}

\newcommand{\freiburg}{\affiliation{Physikalisches Institut, Universität Freiburg, 79104 Freiburg, Germany}}

@@

\title{Search for WIMP Inelastic Scattering Off Xenon Nuclei With XENON100}% Force line breaks with \\
\author{E.~Aprile}\columbia

\author{J.~Aalbers}\nikhef

\author{F.~Agostini}\lngs\bologna

\author{M.~Alfonsi}\mainz

\author{F.~D.~Amaro}\coimbra

\author{M.~Anthony}\columbia

\author{F.~Arneodo}\nyuad

\author{P.~Barrow}\zurich

\author{L.~Baudis}\zurich

\author{B.~Bauermeister}\stockholm

\author{M.~L.~Benabderrahmane}\nyuad

\author{T.~Berger}\rpi

\author{P.~A.~Breur}\nikhef

\author{A.~Brown}\nikhef

\author{E.~Brown}\rpi

\author{S.~Bruenner}\heidelberg

\author{G.~Bruno}\lngs

\author{R.~Budnik}\wis

\author{L.~B\"utikofer}\freiburg\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}

\author{J.~Calv\'en}\stockholm

\author{J.~M.~R.~Cardoso}\coimbra

\author{M.~Cervantes}\purdue

\author{D.~Cichon}\heidelberg

\author{D.~Coderre}\freiburg\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}

\author{A.~P.~Colijn}\nikhef

\author{J.~Conrad}\altaffiliation{Wallenberg Academy Fellow}\stockholm

\author{J.~P.~Cussonneau}\subatech

\author{M.~P.~Decowski}\nikhef

\author{P.~de~Perio}\columbia

\author{P.~Di~Gangi}\bologna

\author{A.~Di~Giovanni}\nyuad

\author{S.~Diglio}\subatech

\author{G.~Eurin}\heidelberg

\author{J.~Fei}\ucsd

\author{A.~D.~Ferella}\stockholm

\author{A.~Fieguth}\munster

\author{W.~Fulgione}\lngs\torino

\author{A.~Gallo Rosso}\lngs

\author{M.~Galloway}\zurich

\author{F.~Gao}\columbia

\author{M.~Garbini}\bologna

\author{C.~Geis}\mainz

\author{L.~W.~Goetzke}\columbia

\author{Z.~Greene}\columbia

\author{C.~Grignon}\mainz

\author{C.~Hasterok}\heidelberg

\author{E.~Hogenbirk}\nikhef

\author{R.~Itay}\wis

\author{B.~Kaminsky}\freiburg\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}

\author{S.~Kazama}\zurich

\author{G.~Kessler}\zurich

\author{A.~Kish}\zurich

\author{H.~Landsman}\wis

\author{R.~F.~Lang}\purdue

\author{D.~Lellouch}\wis

\author{L.~Levinson}\wis

\author{Q.~Lin}\columbia

\author{S.~Lindemann}\heidelberg\freiburg

\author{M.~Lindner}\heidelberg

\author{F.~Lombardi}\ucsd

\author{J.~A.~M.~Lopes}\altaffiliation[Also with ]{Coimbra Engineering Institute, Coimbra, Portugal}\coimbra

\author{A.~Manfredini}\wis

\author{I.~Maris}\nyuad

\author{T.~Marrod\'an~Undagoitia}\heidelberg

\author{J.~Masbou}\subatech

\author{F.~V.~Massoli}\bologna

\author{D.~Masson}\purdue

\author{D.~Mayani}\zurich

\author{M.~Messina}\columbia

\author{K.~Micheneau}\subatech

\author{A.~Molinario}\lngs

\author{K.~Mora}\stockholm

\author{M.~Murra}\munster

\author{J.~Naganoma}\rice

\author{K.~Ni}\ucsd

\author{U.~Oberlack}\mainz

\author{P.~Pakarha}\zurich

\author{B.~Pelssers}\stockholm

\author{R.~Persiani}\subatech

\author{F.~Piastra}\zurich

\author{J.~Pienaar}\purdue

\author{V.~Pizzella}\heidelberg

\author{M.-C.~Piro}\rpi

\author{G.~Plante}\columbia

\author{N.~Priel}\wis

\author{L.~Rauch}\heidelberg

\author{S.~Reichard}\purdue

\author{C.~Reuter}\purdue

\author{A.~Rizzo}\columbia

\author{S.~Rosendahl}\munster

\author{N.~Rupp}\heidelberg

\author{J.~M.~F.~dos~Santos}\coimbra

\author{G.~Sartorelli}\bologna

\author{M.~Scheibelhut}\mainz

\author{S.~Schindler}\mainz

\author{J.~Schreiner}\heidelberg

\author{M.~Schumann}\freiburg

\author{L.~Scotto~Lavina}\paris

\author{M.~Selvi}\bologna

\author{P.~Shagin}\rice

\author{M.~Silva}\coimbra

\author{H.~Simgen}\heidelberg

\author{M.~v.~Sivers}\freiburg\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}

\author{A.~Stein}\ucla

\author{D.~Thers}\subatech

\author{A.~Tiseni}\nikhef

\author{G.~Trinchero}\torino

\author{C.~Tunnell}\nikhef\chicago

\author{M.~Vargas}\munster

\author{H.~Wang}\ucla

\author{Z.~Wang}\lngs

\author{Y.~Wei}\zurich

\author{C.~Weinheimer}\munster

\author{J.~Wulf}\zurich

\author{J.~Ye}\ucsd

\author{Y.~Zhang.}\columbia

\collaboration{XENON Collaboration}\email{xenon@lngs.infn.it}\noaffiliation

@@

%\input{appendix}

### 2017-04-24 Inelastic/intro.tex
add all comments, final version

We consider the $^{129}\text{Xe}$ isotope, which has an abundance of 26.4\% in natural xenon, and a lowest-lying 
3/2$^{+}$ state at 36.6\,keV above the 1/2$^+$ ground state. The electromagnetic nuclear decay has a half-life of 0.97\,ns. 
The signatures and structure functions for inelastic scattering in xenon have been studied in detail in~\cite{Baudis:2013bba}. It was found that this channel is complementary to spin-dependent, elastic scattering, and that it dominates the integrated rates above $\simeq10$\,keV of deposited energy. 
In addition, in case of a positive signal, the observation of inelastic scattering would provide a clear 
indication of the spin-dependent nature of the fundamental interaction.

@@

XENON100 has acquired science data between 2008-2015, and has set competitive constraints on spin-independent~\cite{Aprile:2012nq,Aprile:2016swn} 
and spin-dependent~\cite{Aprile:2013doa,Aprile:2016swn} elastic WIMP-nucleus 
scatters, on solar axions and galactic ALPs~\cite{Aprile:2014eoa}, as well as on leptophilic dark matter models~\cite{Aprile:2015ade,Aprile:2015ibr,Aprile:2017yea}. 
%%%% possible to be CUTTED %%%%%%%%% 
%that were invented to explain the annual modulation signature observed in the DAMA/LIBRA experiment~\cite{Bernabei:2012in}.

>>>>

We consider the $^{129}\text{Xe}$ isotope, which has an abundance of 26.4\% in natural xenon, and a lowest-lying 
3/2$^{+}$ state at 36.9\,keV above the 1/2$^+$ ground state. The electromagnetic nuclear decay has a half-life of 0.97\,ns. 
The signatures and structure functions for inelastic scattering in xenon have been studied in detail in~\cite{Baudis:2013bba}. It was found that this channel is complementary to spin-dependent, elastic scattering, and that it dominates the integrated rates above $\simeq10$\,keV of deposited energy. 
In addition, in case of a positive signal, the observation of inelastic scattering would provide a clear 
indication of the spin-dependent nature of the fundamental interaction.

@@

XENON100 has acquired science data between 2009-2015, and has set competitive constraints on spin-independent~\cite{Aprile:2012nq,Aprile:2016swn} 
and spin-dependent~\cite{Aprile:2013doa,Aprile:2016swn} elastic WIMP-nucleus 
scatters, on solar axions and galactic ALPs~\cite{Aprile:2014eoa}, as well as on leptophilic dark matter models~\cite{Aprile:2015ade,Aprile:2015ibr,Aprile:2017yea}. 
%%%% possible to be CUTTED %%%%%%%%% 
%that were invented to explain the annual modulation signature observed in the DAMA/LIBRA experiment~\cite{Bernabei:2012in}.

### 2017-04-24 Inelastic/results.tex
add all comments, final version

While these upper limits are not competitive to spin-dependent, elastic scattering results, as obtained by XENON100~\cite{Aprile:2013doa} and LUX~\cite{Akerib:2016lao} 
(bounding the cross section to be $<\,2 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/c$^2$ WIMP), 
%(with a cross section minimum of $\sim2 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/c$^2$ WIMP), 
our results are the most stringent for the spin-dependent inelastic channel, and set the stage for a sensitive search of inelastic WIMP-nucleus scattering in running or upcoming liquid xenon experiments such as XENON1T~\cite{Aprile:2015uzo}, XENONnT~\cite{Aprile:2015uzo},  LZ~\cite{Akerib:2015cja}, and DARWIN~\cite{Aalbers:2016jon}. In these larger detectors, with lower intrinsic backgrounds from $^{85}$Kr and $^{222}$Rn decays, and improved self-shielding, the electronic recoil background will be reduced by a few orders of magnitude with respect to XENON100, and ultimately limited by solar neutrino interactions~\cite{Baudis:2013qla}. 
The discovery of this interaction channel would be a clear signature for a spin-dependent nature of the dark matter interaction, and would provide a potential handle  to constrain the WIMP mass with data from one experiment only~\cite{Baudis:2013bba,McCabe:2016aof}.

>>>>

While these upper limits are not competitive to spin-dependent, elastic scattering results, as obtained by XENON100~\cite{Aprile:2013doa} and LUX~\cite{Akerib:2016lao} 
(bounding the cross section to be $<\,1 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/c$^2$ WIMP), 
%(with a cross section minimum of $\sim2 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/c$^2$ WIMP), 
our results are the most stringent for the spin-dependent inelastic channel, and set the stage for a sensitive search of inelastic WIMP-nucleus scattering in running or upcoming liquid xenon experiments such as XENON1T~\cite{Aprile:2015uzo}, XENONnT~\cite{Aprile:2015uzo},  LZ~\cite{Akerib:2015cja}, and DARWIN~\cite{Aalbers:2016jon}. In these larger detectors, with lower intrinsic backgrounds from $^{85}$Kr and $^{222}$Rn decays, and improved self-shielding, the electronic recoil background will be reduced by a few orders of magnitude with respect to XENON100, and ultimately limited by solar neutrino interactions~\cite{Baudis:2013qla}. 
The discovery of this interaction channel would be a clear signature for a spin-dependent nature of the dark matter interaction, and would provide a potential handle  to constrain the WIMP mass with data from one experiment only~\cite{Baudis:2013bba,McCabe:2016aof}.
